Maximum Entropy Spectral Analysis: a case study

### 2021-05-26 paper/referee_response.md

- I’m not sure if this qualifies as a PnP comment, but a significant omission is the lack of discussion of the Bayeswave method of PSD estimation, which is the official method for calculating PSDs for parameter estimation results by the LVC. In addition to citing the papers described above, I think it would be appropriate to add a discussion, either in the Introduction or the Final Remarks comparing MESA to this “on-source” PSD estimation and citing the relvant papers disucssing the Bayeswave PSD method in comparison to the Welch method, some repeated from the above requests (1907.06540, 2006.05292).
	+ Work in progress: This is a very good suggestion... Are we gonna include BayesLine among our comparison? It looks like a good idea. If we do so, probably we want to say something about it in the beginning.The paper 1907.06540 is already cited together with BayesWave

## Personal comments

We fixed all the typos that the referee pointed out. We are thankful for that.

### Validations of the model:
- I wasn't able to get a good grasp of the practical applications of the estimation of the autoregressive process order while reading this section. Is gravitational-wave data expected to be stationary enough to reliably model as an autoregressive process? If not, what are some other examples? It would be very helpful to elaborate on this, perhaps when the connection to AR is introduced.
	+ Work in progress: I guess we could just point out that it is just a way to validate the accuracy of the method and to test which loss function is better. Does it makes sense?

@@

- It’s not really clear to me when you perform the forecasting for the temperature data why CAT is the obvious choice for the loss function, since in the previous section you described how CAT is unable to recover the true order of the autoregressive process. Does that mean that it would be worse at forecasting based on the AR(p)? There seems to be a contradiction where CAT does a better job for the temperature data but worse for the simulation presented in section II. It would be helpful to elaborate on this.
	+ We added a claryfing footnote on this (note 10, page 13). We hope it is clear.

- "Indeed, a precise prediction of the strain time series can be beneficial in the detection of anomalies in the data and, eventually, their removal.”: How does this compare to the method presented in https://arxiv.org/abs/1908.05644, where the data containing a glitch are “inpainted” with values chosen such that the inverse-PSD-filtered data is 0 at these times?
	+ Work in progress: we should understand what's in the paper...

### Final Remarks and Future Prospects

- In addition to adding the citations to other LVC works presenting methods and results for marginalizing over the PSD uncertainty (see PnP comments above), a more detailed discussion of how MESA compares to these other methods (particularly the error in the PSD measurement) would be appropriate here.
	+ Work in progress: shall we quote some numbers about the accuracy? Or we just reitarete the qualitative findings we had?
